The cut operation on matrix factorisations

### 2016-11-02 cutsystems-new.tex
Typos

\title{Cut systems and matrix factorisations I}
\author{Daniel Murfet}

@@

The bicategory $\LG$ of Landau-Ginzburg models has a rich structure, attested to by the existence of adjoints and pivotality \cite{lgdual}, its role in recent important results in topological field theory \cite{genorb,ade} and the theory of homological knot invariants \cite{kr0401268}. This is remarkable in light of the fact that $1$-morphisms are very simple objects, namely, matrices of polynomials which satisfy an equation. This makes $\LG$ an attractive object of study, but for one major wrinkle: the composition operation for $1$-morphisms is infinitary.

The objects of $\LG$ are a class of polynomials $W(x)$ called potentials, and $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$. Such a matrix factorisation is a $\nZ_2$-graded free $\nC[x,y]$-module $X = X^0 \oplus X^1$ together with an odd operator $d_X$ satisfying $d_X^2 = (V(y) - W(x)) \cdot 1_X$. These $1$-morphisms form a category denoted $\LG(W,V)$. For a third potential $U(z)$, composition is a functor
\begin{gather*}
\LG(V,U) \times \LG(W,V) \lto \LG(W,U)\,,\\
(Y , X) \mapsto Y \circ X
\end{gather*}
% In this paper and its sequel we study an enrichment of $\LG$ which we refer to as a \emph{cut system}.
defined for matrix factorisations $Y$ of $V - U$ and $X$ of $W - V$ by
\be
Y \circ X = \big( Y \otimes_{\nC[y]} X, d_Y \otimes 1 + 1 \otimes d_X \big)\,.
\ee
This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $\nC[x,z]$, which is only homotopy equivalent to a finite rank matrix factorisation. While this finite model can be proven abstractly to exist, there is no obvious way to describe it as a function of the input data $Y,X$. This means that we are stuck with infinite rank matrix factorisations in the theory.

Together with Dyckerhoff we initiated in \cite{dm1102.2957} the study of these finite models in terms of homological perturbation and Atiyah classes, and in the present paper this program reaches its logical conclusion. We introduce a bicategory $\L$ in which the objects are again potentials and the $1$-morphisms $W \lto V$ are finite rank matrix factorisations of $V - W$ additionally equipped with the structure of a representation of a Clifford algebra. This bicategory is equivalent to $\LG$, but it is simpler: the composition operation is described by a finite number of polynomial functions of the input data. More precisely, the composition of $1$-morphisms in $\L$ is a functor
\begin{gather}
\L(V,U) \times \L(W,V) \lto \L(W,U)\,,\label{eq:cut_functor_intro}\\
(Y,X) \mapsto Y \l X
\end{gather}
which we call the \emph{cut operation}. Let us describe the cut in the most important case, where $Y, X$ are matrix factorisations as above, not equipped with any additional structure as representations of a Clifford algebra. The Jacobi algebra $J_V = \nC[y_1,\ldots,y_m]/(\partial_{y_1} V, \ldots, \partial_{y_m} V)$ is a finite-dimensional $\nC$-vector space by the assumption that $V(y)$ is a potential, and the cut is defined to be the following finite rank matrix factorisation over $\nC[x,z]$
\be
Y \l X = Y \otimes_{\nC[y]} J_V \otimes_{\nC[y]} X = ( Y \otimes_{\nC[y]} X ) / (\partial V) (Y \otimes_{\nC[y]} X )
\ee
equipped with a family of odd closed operators $\{\ferm_i, \fermc_i\}_{i=1}^m$ defined by
\begin{equation}\label{eq:intro_clifford_act1_intro}
\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}
\end{equation}
where the $\At_q$ are Atiyah classes. These operators satisfy Clifford relations
\be\label{eq:clifford_relations_intro}
\ferm_i \ferm_j + \ferm_j \ferm_i = 0, \qquad \fermc_i \fermc_j + \fermc_j \fermc_i = 0, \qquad \ferm_i \fermc_j + \fermc_j \ferm_i = \delta_{ij}
\ee
up to homotopy (see Theorem \ref{theorem:cut_is_rep}). The differential on $Y \l X$ and the Clifford operators can be written explicitly as matrices over $\nC[x,z]$, where the coefficients of the monomials in each row and column are polynomials in the monomial coefficients of $d_Y, d_X$ and $V$. Thus, the cut operation is a polynomial function of its inputs and, in particular, infinite rank matrix factorisations are banished.

Let us sketch where the cut operation comes from, why Clifford algebras are involved, and why there is an equivalence $\L \cong \LG$. In Section \ref{section:intro_appli} we describe various applications. The main theorem (Theorem \ref{theorem:htpy_equivalence_main}) uses homological perturbation to produce a strong deformation retract, and in particular an isomorphism, in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $\nC[x,z]$ of the form
\begin{equation}\label{eq:final_finite_model_intro}
\xymatrix@C+4pc{
Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{\nC} ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
}
\end{equation}
where $S_m = \bigwedge ( \nC^{\oplus m}[1] )$ denotes the exterior algebra. The algebra $C_m = \End_{\nC}(S_m)$ is a Clifford algebra, and \eqref{eq:final_finite_model_intro} identifies the natural action of $C_m$ on the right hand side with the action of $C_m$ via the aforementioned operators $\ferm_i, \fermc_i$ on the left hand side.

There is a category called the \emph{Clifford thickening} of the homotopy category of matrix factorisations of $U - W$, in which objects are matrix factorisations equipped with a $C_k$-action for some $k$ (i.e. $k$ is allowed to be different for different objects). In this category $S_m \otimes_{\nC} ( Y \otimes X )$ with its $C_m$-action is isomorphic to $Y \otimes X$ with no Clifford action, and so \eqref{eq:final_finite_model_intro} can be read as a natural isomorphism $Y \l X \cong Y \otimes X$. We prove this is suitably functorial in $Y,X$ and therefore defines an equivalence $\L \cong \LG$.

@@

\subsubsection{Cut systems: a geometric enrichment of $\LG$}

The \emph{cut systems} of the title are bicategories enriched over affine schemes. Our primary motivation for introducing $\cat{C}$ is that it can be enriched in this way (whereas $\LG$ cannot, because the composition is infinitary). For context we sketch the definition of a cut system here; the full definition will appear in a sequel to the present paper.

Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
\be\label{eq:intro_capitalD}
D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
\ee
where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices. If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the $\nC$-points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.

@@

In forthcoming work we use the cut system enrichment of $\L$ to define a semantics of linear logic \cite{girard_llogic} in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential. Proofs in the logic are interpreted by certain correspondences between these pairs. Let us briefly explain the general point which leads us to use $\L$ rather than $\LG$, for which we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).

@@

A superbicategory has for every $1$-morphism $F$ an associated $1$-morphism $\Psi F$ with $\Psi^2 \cong 1$, and in this sense the categories of $1$-morphisms are $\mathbb{Z}_2$-graded. The bicategory of Landau-Ginzburg models is an example of a superbicategory. Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role in the definition of cut systems, superbicategories are the natural language. Our main references for the foundations are \cite{ellis_lauda,kang,kang2}, but we give the full definitions below as these references work only with strict bicategories.

@@

\begin{remark}\label{remark:relation_to_toby_paper} The cut system presented here refines earlier work in \cite{dm1102.2957}. To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$. The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is 
\[
e_m' = \fermc_1 \cdots \fermc_m \ferm_m \cdots \ferm_1\,.
\]
Observe that each of the $\fermc_i$'s acts as $- \partial_{y_i}(d_X)$ because all of the $\ferm_j$'s to the right. Hence
\begin{align*}
e_m' &= (-1)^{\binom{m}{2}} \fermc_1 \cdots \fermc_m \ferm_1 \cdots \ferm_m \\
&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
\end{align*}
which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.

@@

The more common statement of the basic perturbation lemma involves the deformation retract corresponding to the splitting homotopy $\phi_\infty$ under the equivalence of Lemma \ref{lemma:equivocate}. The statement is that given a splitting homotopy $\phi$ as above with associated deformation retract \eqref{eq:defn_sdr} there is a strong deformation retract
\begin{equation}\label{eq:perturbedsdr}
\xymatrix@C+2pc{
(M,d_\infty) \ar@<-1ex>[r]_{\sigma_\infty} & (A, \xi), \ar@<-1ex>[l]_{\pi_\infty}
} \quad \phi_\infty
\end{equation}
where $A = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
\begin{align*}
\sigma_\infty &= \sigma - \phi A \sigma,\\
\pi_\infty &= \pi - \pi A \phi,\\
d_\infty &= d + \pi A \sigma\,.
\end{align*}
As explained in \cite{barneslambe}, to derive these formulas one has only to notice that the sub-complex in the deformation retract associated to $\phi_\infty$ can, by the isomorphism
\[
\im(1 - [\xi, \phi_\infty]) \cong \im(e) = M
\]
be identified with $M$, and the induced maps are the $\sigma_\infty, \pi_\infty, d_\infty$ given above. It is also possible to give a direct proof as in \cite{crainic}. %To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.

@@

Eventually we are going to substitute $a_i = \lambda_i, b_i = \theta_i^*$ so that $D = \delta$, and we will take further $c = \gamma$. In this notation, the aim of all of this is to compute the commutators $[c, D^n]$ and then $[c, \exp(-D)]$. Since most of the calculation can be done in $A$, so we stick to the general setting as long as possible, and maintain the notation $a_i, b_i, c, D$ and \eqref{defn:tau}, \eqref{defn:bq} of the previous lemma.

@@

This appendix collects the data needed for constructing a superbicategory $\cat{B}$ from a collection of supercategories $\cat{B}(a,b)$. Given a bicategory $\cat{B}$ and for each pair of objects $a,b$ the structure of a supercategory on $\cat{B}(a,b)$, we denote composition by
\[
T: \cat{B}(a, b) \otimes_k \cat{B}(b,c) \lto \cat{B}(a,c)\,.
\]
Since our main example is constructing the superbicategory associated to a cut system, we write $T(X,Y)$ as $Y \l X$. We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.

>>>>

\title{The cut operation on matrix factorisations}
\author{Daniel Murfet}

@@

The bicategory $\LG$ of Landau-Ginzburg models has a rich structure, attested to by the existence of adjoints and pivotality \cite{lgdual}, its role in recent important results in topological field theory \cite{genorb,ade} and the theory of homological knot invariants \cite{kr0401268}. While the objects and $1$-morphisms of $\LG$ are very simple, the composition operation for $1$-morphisms has an ``infinitary'' character. This paper continues the study of this operation begun in \cite{dm1102.2957}.

The objects of $\LG$ are a class of polynomials $W(x)$ called potentials, and $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$. Such a matrix factorisation is a $\nZ_2$-graded free $\nC[x,y]$-module $X = X^0 \oplus X^1$ together with an odd operator $d_X$ satisfying $d_X^2 = (V(y) - W(x)) \cdot 1_X$. These $1$-morphisms form a category denoted $\LG(W,V)$. For a third potential $U(z)$, composition is a functor
\begin{gather*}
\LG(V,U) \times \LG(W,V) \lto \LG(W,U)\,,\\
(Y , X) \mapsto Y \circ X
\end{gather*}
% In this paper and its sequel we study an enrichment of $\LG$ which we refer to as a \emph{cut system}.
defined for matrix factorisations $Y$ of $V - U$ and $X$ of $W - V$ by
\be
Y \circ X = \big( Y \otimes_{\nC[y]} X, d_Y \otimes 1 + 1 \otimes d_X \big)\,.
\ee
This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $\nC[x,z]$, which is only homotopy equivalent to a finite rank matrix factorisation. While this finite model can be proven abstractly to exist \cite{dm1102.2957} there is no obvious way to describe it as an explicit function of the input data $Y,X$. This means that we are stuck with infinite rank matrix factorisations in the theory.

Together with Dyckerhoff we initiated in \cite{dm1102.2957} the study of these finite models in terms of homological perturbation and Atiyah classes, and in the present paper this program reaches its logical conclusion. We introduce a bicategory $\L$ in which the objects are again potentials and the $1$-morphisms $W \lto V$ are finite rank matrix factorisations of $V - W$ additionally equipped with the structure of a representation of a Clifford algebra. This bicategory is equivalent to $\LG$, but it is simpler: the composition operation is described by a finite number of polynomial functions of the input data. More precisely, the composition of $1$-morphisms in $\L$ is a functor
\begin{gather}
\L(V,U) \times \L(W,V) \lto \L(W,U)\,,\label{eq:cut_functor_intro}\\
(Y,X) \mapsto Y \l X
\end{gather}
which we call the \emph{cut operation}. Let us describe the cut in the most important case, where $Y, X$ are matrix factorisations as above, not equipped with any additional structure as representations of a Clifford algebra. The Jacobi algebra $J_V = \nC[y_1,\ldots,y_m]/(\partial_{y_1} V, \ldots, \partial_{y_m} V)$ is a finite-dimensional $\nC$-vector space by the assumption that $V(y)$ is a potential, and the cut is defined to be the following finite rank matrix factorisation over $\nC[x,z]$
\be
Y \l X = Y \otimes_{\nC[y]} J_V \otimes_{\nC[y]} X = ( Y \otimes_{\nC[y]} X ) / (\partial V) (Y \otimes_{\nC[y]} X )
\ee
equipped with a family of odd closed operators $\{\ferm_i, \fermc_i\}_{i=1}^m$ defined by
\begin{equation}\label{eq:intro_clifford_act1_intro}
\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}
\end{equation}
where the $\At_q$ are Atiyah classes and $\partial_{y_i} = \frac{\partial}{\partial y_i}$. These operators satisfy Clifford relations
\be\label{eq:clifford_relations_intro}
\ferm_i \ferm_j + \ferm_j \ferm_i = 0, \qquad \fermc_i \fermc_j + \fermc_j \fermc_i = 0, \qquad \ferm_i \fermc_j + \fermc_j \ferm_i = \delta_{ij}
\ee
up to homotopy (see Theorem \ref{theorem:cut_is_rep}). The differential on $Y \l X$ and the Clifford operators can be written explicitly as matrices over $\nC[x,z]$, where the coefficients of the monomials in each row and column are polynomials in the monomial coefficients of $d_Y, d_X$ and $V$. Thus, the cut operation is a polynomial function of its inputs and, in particular, infinite rank matrix factorisations do not appear in the definition of $\L$.

Let us sketch where the cut operation comes from, why Clifford algebras are involved, and why there is an equivalence $\L \cong \LG$. In Section \ref{section:intro_appli} we describe various applications. By the results of \cite{dm1102.2957} there is an isomorphism in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $\nC[x,z]$ of the form
\begin{equation}\label{eq:final_finite_model_intro}
\xymatrix@C+4pc{
Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{\nC} ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
}
\end{equation}
where $S_m = \bigwedge ( \nC^{\oplus m}[1] )$ denotes the exterior algebra on a $\nZ_2$-graded vector space. The algebra $C_m = \End_{\nC}(S_m)$ is a Clifford algebra. The main theorem of the present paper (Theorem \ref{theorem:htpy_equivalence_main}) identifies the natural action of $C_m$ on the right hand side of \eqref{eq:final_finite_model_intro} with the action of $C_m$ via the aforementioned operators $\ferm_i, \fermc_i$ on the left hand side.

There is a category called the \emph{Clifford thickening} of the homotopy category of matrix factorisations of $U - W$, in which objects are matrix factorisations equipped with a $C_l$-action for some $l$ (i.e. $l$ is allowed to be different for different objects). In this category $S_m \otimes_{\nC} ( Y \otimes X )$ with its $C_m$-action is isomorphic to $Y \otimes X$ with no Clifford action, and so \eqref{eq:final_finite_model_intro} can be read as a natural isomorphism $Y \l X \cong Y \otimes X$. We prove this is suitably functorial in $Y,X$ and therefore defines an equivalence $\L \cong \LG$.

@@

\subsubsection{A geometric enrichment of $\LG$}

Our primary motivation for introducing $\cat{C}$ is that it can be enriched over affine schemes; this is not true directly of $\LG$, because the composition is infinitary. For context we include a sketch. Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
\be\label{eq:intro_capitalD}
D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
\ee
where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices. If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the $\nC$-points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.

@@

In forthcoming work we use the above enrichment of $\L$ to define a semantics of linear logic \cite{girard_llogic} in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential. Proofs in the logic are interpreted by certain correspondences between these pairs. Let us briefly explain the general point which leads us to use $\L$ rather than $\LG$, for which we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).

@@

A superbicategory has for every $1$-morphism $F$ an associated $1$-morphism $\Psi F$ with $\Psi^2 \cong 1$, and in this sense the categories of $1$-morphisms are $\mathbb{Z}_2$-graded. The bicategory of Landau-Ginzburg models is an example of a superbicategory. Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role, superbicategories are the natural language. Our main references for the foundations are \cite{ellis_lauda,kang,kang2}, but we give the full definitions below as these references work only with strict bicategories.

@@

\begin{remark}\label{remark:relation_to_toby_paper} The cut operation presented here refines earlier work in \cite{dm1102.2957}. To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$. The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is 
\[
e_m' = \fermc_1 \cdots \fermc_m \ferm_m \cdots \ferm_1\,.
\]
Observe that each of the $\fermc_i$'s acts as $- \partial_{y_i}(d_X)$ because all of the $\ferm_j$'s to the right. Hence
\begin{align*}
e_m' &= (-1)^{\binom{m}{2}} \fermc_1 \cdots \fermc_m \ferm_1 \cdots \ferm_m \\
&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
\end{align*}
which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.

@@

The more common statement of the basic perturbation lemma involves the deformation retract corresponding to the splitting homotopy $\phi_\infty$ under the equivalence of Lemma \ref{lemma:equivocate}. The statement is that given a splitting homotopy $\phi$ as above with associated deformation retract \eqref{eq:defn_sdr} there is a strong deformation retract
\begin{equation}\label{eq:perturbedsdr}
\xymatrix@C+2pc{
(M,d_\infty) \ar@<-1ex>[r]_{\sigma_\infty} & (A, \xi), \ar@<-1ex>[l]_{\pi_\infty}
} \quad \phi_\infty
\end{equation}
where $C = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
\begin{align*}
\sigma_\infty &= \sigma - \phi C \sigma,\\
\pi_\infty &= \pi - \pi C \phi,\\
d_\infty &= d + \pi C \sigma\,.
\end{align*}
As explained in \cite{barneslambe}, to derive these formulas one has only to notice that the sub-complex in the deformation retract associated to $\phi_\infty$ can, by the isomorphism
\[
\im(1 - [\xi, \phi_\infty]) \cong \im(e) = M
\]
be identified with $M$, and the induced maps are the $\sigma_\infty, \pi_\infty, d_\infty$ given above. It is also possible to give a direct proof as in \cite{crainic}. %To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.

@@

Eventually we are going to substitute $a_i = \lambda_i, b_i = \theta_i^*$ so that $D = \delta$, and we will take further $c = \gamma$. In this notation, the aim of all of this is to compute the commutators $[c, D^n]$ and then $[c, \exp(-D)]$. Since most of the calculation can be done in $A$, we stick to the general setting as long as possible, and maintain the notation $a_i, b_i, c, D$ and \eqref{defn:tau}, \eqref{defn:bq} of the previous lemma.

@@

This appendix collects the data needed for constructing a superbicategory $\cat{B}$ from a collection of supercategories $\cat{B}(a,b)$. Given a bicategory $\cat{B}$ and for each pair of objects $a,b$ the structure of a supercategory on $\cat{B}(a,b)$, we denote composition by
\[
T: \cat{B}(a, b) \otimes_k \cat{B}(b,c) \lto \cat{B}(a,c)\,.
\]
Since our main example is constructing the superbicategory associated to the cut operation, we write $T(X,Y)$ as $Y \l X$. We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.
